The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-02-19 paper/ms.tex
Split sample properties from observation log

The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time. It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}. Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the potential sample. We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models. Finally, we exclude post-main sequence stars from our sample because the binary flux ratio would be even less favorable to companion detection in an evolved star. Most of the spectral peculiarities denote narrow lines, which are already removed from the sample by the $v\sin{i}$ cut. The target list and observing details are given in Table \ref{tab:observations}.

@@

@@

\LongTables
\begin{deluxetable*}{|l|lllrlrr|}
\tabletypesize{\small}
\tablewidth{0pt}
\tablecaption{Target Lists and Observation Log}
\tablehead{
      \colhead{} & \colhead{} & \colhead{} & \colhead{} &  \colhead{MJD} & \colhead{}  & \colhead{exptime} & \colhead{} \\
       \colhead{star} & \colhead{SpT} & \colhead{RA} & \colhead{DEC} &  \colhead{(JD-2450000)} &   \colhead{instrument} & \colhead{(sec)} & \colhead{snr}
       }

@@

     HIP 813 &           B9Vn &     00:10:2.20 &   +11:08:44.93 &  6618.58 &       TS23 &      557 &  1810 \\
    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &  6552.60 &     CHIRON &     1200 &   320 \\
    HIP 1366 &            A2V &     00:17:5.50 &   +38:40:53.89 &  6585.73 &       TS23 &      274 &  1790 \\
    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &  6510.74 &     CHIRON &     1105 &   630 \\
    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &  6874.71 &     CHIRON &      505 &   580 \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6586.71 &       TS23 &      235 &  1700 \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6962.71 &       TS23 &      804 &  1960 \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &  6945.71 &     IGRINS &      224 &   210 \\
    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  7240.93 &     IGRINS &      360 &   100 \\
    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &  6516.84 &        HRS &      412 &  1070 \\
    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  7238.96 &     IGRINS &      367 &   130 \\
    HIP 2912 &            B5V &    00:36:52.85 &    +33:43:9.64 &  6583.78 &       TS23 &      199 &  2460 \\
    HIP 3300 &            B2V &     00:42:3.90 &   +50:30:45.09 &  6299.55 &       TS23 &      689 &  1010 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6963.63 &       TS23 &     1200 &  1020 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  7288.82 &     IGRINS &      540 &    30 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6669.53 &       TS23 &      743 &  1870 \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &  6945.72 &     IGRINS &      224 &   150 \\
    HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7174.89 &     CHIRON &     3981 &   430 \\
    HIP 3741 &            B9V &     00:48:1.06 &   -21:43:20.99 &  7175.90 &     CHIRON &     3561 &   420 \\
    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6585.70 &       TS23 &      222 &  1690 \\
    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6964.60 &       TS23 &     1200 &   710 \\
    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &  6945.74 &     IGRINS &      224 &   200 \\
    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &  6585.76 &       TS23 &      129 &  1940 \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6587.70 &       TS23 &      655 &  1780 \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  7083.57 &     IGRINS &      930 &    70 \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &  6847.89 &     IGRINS &     1600 &   110 \\
    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6587.77 &       TS23 &      535 &  1550 \\
    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &  6847.89 &     IGRINS &      480 &   110 \\
    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &  6945.75 &     IGRINS &      224 &   200 \\
    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &  6523.84 &        HRS &     1000 &   810 \\
    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  7238.94 &     IGRINS &      540 &    80 \\
    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &  6945.77 &     IGRINS &      224 &   160 \\
    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &  6945.88 &     IGRINS &      224 &   160 \\
    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6888.76 &     CHIRON &     1080 &   480 \\
    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &  6887.76 &     CHIRON &      706 &   540 \\
    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &  6522.96 &        HRS &      328 &   580 \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  6506.90 &        HRS &      365 &   420 \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7084.57 &     IGRINS &      960 &    30 \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &  7237.93 &     IGRINS &      720 &    90 \\
      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6668.56 &       TS23 &      597 &  1920 \\
      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6586.75 &       TS23 &      265 &  1710 \\
      HR 545 &            B9V &    01:53:31.77 &   +19:17:46.27 &  6945.81 &     IGRINS &      224 &   230 \\
    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &  6586.78 &       TS23 &      419 &  1750 \\
    HIP 9564 &           A1Vn &    02:02:52.48 &    +64:54:5.27 &  6945.78 &     IGRINS &      224 &   140 \\
      HR 604 &        B8V+A0V &    02:03:54.72 &   +42:19:51.41 &  6585.86 &       TS23 &      349 &  1650 \\
   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &  6532.80 &     CHIRON &     1020 &   550 \\
   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &  6618.68 &       TS23 &      141 &  1810 \\
   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  6945.82 &     IGRINS &      224 &   180 \\
   HIP 10732 &           A1Vn &     02:18:7.54 &    +19:54:4.19 &  7083.56 &     IGRINS &      240 &   110 \\
   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &  6894.90 &     CHIRON &      540 &   520 \\
   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6677.54 &       TS23 &     1107 &  1530 \\
   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &  6947.79 &     IGRINS &      224 &   170 \\
   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6584.86 &       TS23 &      362 &   990 \\
   HIP 12706 &       A2Vn+F4V &    02:43:18.04 &    +03:14:8.94 &  6946.84 &     IGRINS &      224 &   150 \\
   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &  6583.87 &       TS23 &      264 &  1720 \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6676.53 &       TS23 &      452 &  1410 \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  6947.80 &     IGRINS &      224 &   140 \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &  7240.95 &     IGRINS &      780 &   120 \\
   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &  6518.91 &        HRS &      275 &   850 \\
   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &  6910.83 &     CHIRON &      580 &   570 \\
   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &  6618.66 &       TS23 &      143 &  1880 \\
   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &  6670.54 &       TS23 &     1200 &  1800 \\
   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6917.83 &     CHIRON &      644 &   550 \\
   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &  6970.75 &     CHIRON &      703 &   550 \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6945.79 &     IGRINS &      224 &   260 \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6681.68 &       TS23 &      930 &   230 \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &  6618.70 &       TS23 &      265 &  1490 \\
   HIP 14043 &            B7V &    03:00:52.21 &    +52:21:6.22 &  6523.92 &        HRS &      400 &   620 \\
   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &  6518.94 &        HRS &      462 &   900 \\
   HIP 14293 &            A5V &    03:04:16.52 &    -07:36:3.08 &  6919.89 &     CHIRON &      800 &   240 \\
   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &  6583.83 &       TS23 &       40 &  1030 \\
   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &  6582.92 &       TS23 &       36 &  2050 \\
   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6679.53 &       TS23 &      532 &  1370 \\
   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &  6946.80 &     IGRINS &      360 &   150 \\
   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  6945.86 &     IGRINS &      224 &   180 \\
   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &  7084.60 &     IGRINS &     1200 &   120 \\
   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &  6946.83 &     IGRINS &      224 &   120 \\
   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &  6523.90 &        HRS &      570 &   690 \\
   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &  6517.92 &        HRS &      205 &   620 \\
   HIP 15444 &            B5V &     03:19:7.64 &   +50:05:41.88 &  6582.94 &       TS23 &      340 &  1790 \\
   HIP 16147 &            B5V &     03:28:3.07 &   +49:03:46.32 &  6299.59 &       TS23 &      735 &  1300 \\
   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6676.58 &       TS23 &      406 &  1440 \\
   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &  6945.84 &     IGRINS &      224 &   160 \\
   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6583.84 &       TS23 &      311 &  1750 \\
   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &  6945.83 &     IGRINS &      224 &   230 \\
   HIP 16285 &            A5V &    03:29:55.15 &    -42:38:3.32 &  6933.84 &     CHIRON &      767 &   570 \\
   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6944.72 &     CHIRON &      680 &   410 \\
   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &  6946.82 &     IGRINS &      224 &   170 \\
   HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &  6678.54 &       TS23 &      570 &  1410 \\
   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &  6945.85 &     IGRINS &      224 &   170 \\
   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6946.85 &     IGRINS &      224 &   210 \\
   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &  6522.88 &     CHIRON &      255 &   580 \\
   HIP 17457 &           B7IV &    03:44:30.51 &   -01:09:47.14 &  6531.82 &     CHIRON &     1005 &   520 \\
   HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &  6538.82 &     CHIRON &     1088 &   400 \\
   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6947.82 &     IGRINS &      224 &   120 \\
   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6517.93 &        HRS &      429 &   670 \\
   HIP 17527 &            B8V &     03:45:9.74 &   +24:50:21.34 &  6963.91 &       TS23 &      818 &   470 \\
   HIP 18141 &            B8V &    03:52:41.66 &   -05:21:40.54 &  6678.59 &       TS23 &      605 &  1430 \\
   HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &  6516.94 &        HRS &      259 &   510 \\
   HIP 18724 &            B3V &    04:00:40.82 &   +12:29:25.22 &  6299.62 &       TS23 &      226 &  1220 \\
   HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &  6535.81 &     CHIRON &     1039 &   180 \\
   HIP 18805 &            B5V &    04:01:46.14 &   +09:59:52.84 &  6585.78 &       TS23 &      631 &  1760 \\
   HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &  6668.63 &       TS23 &     1200 &  1900 \\
   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  6945.90 &     IGRINS &      224 &   220 \\
   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &  7084.62 &     IGRINS &      960 &    30 \\
   HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &  6676.62 &       TS23 &      524 &  1390 \\
   HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &  6718.53 &     CHIRON &      860 &   410 \\
   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  6945.89 &     IGRINS &      224 &   180 \\
   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &  7084.67 &     IGRINS &     1200 &    30 \\
   HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &  6520.95 &        HRS &      360 &   710 \\
   HIP 20507 &            A2V &    04:23:40.85 &   -03:44:43.68 &  6719.50 &     CHIRON &      715 &   470 \\
   HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &  6517.96 &        HRS &      490 &   830 \\
   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6946.86 &     IGRINS &      224 &   150 \\
   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &  6586.83 &       TS23 &      524 &  1610 \\

>>>>

The magnitude limit ensures that a sufficiently high signal-to-noise ratio can be achieved in a short period of time. It does introduce a Malmquist bias in the derived mass ratio, which we discuss and correct for in Section \ref{sec:mrd}. Likewise, the $v\sin{i}$ limit makes accounting for the primary star spectrum in the companion search trivial; since most A- or B-type stars are rapid rotators, the cutoff does not remove very many stars from the potential sample. We exclude pre-main sequence stars because both the primary and the companion mass would depend very strongly on young and uncertain ($\lesssim 1$ Myr) evolutionary models. Finally, we exclude post-main sequence stars from our sample because the binary flux ratio would be even less favorable to companion detection in an evolved star. Most of the spectral peculiarities denote narrow lines, which are already removed from the sample by the $v\sin{i}$ cut. The sample is given in Table \ref{tab:sample}.

@@

We give the spectroscopic observation log in Table \ref{tab:observations}. We calculate the signal-to-noise ratio (the "snr" column) for the optical instruments (CHIRON, TS23, and HRS) as the median of the extracted flux divided by it's uncertainty for each pixel from the \'echelle order nearest $675$ nm. For the IGRINS instrument, we calculate the signal-to-noise ratio from the order nearest $2200$ nm.

@@

\LongTables
\begin{deluxetable*}{|l|lrrrrllllll|}
\tabletypesize{\scriptsize}
\tablewidth{0pt}
\tablecaption{Sample Properties}
\tablehead{
      \colhead{} & \colhead{} & \colhead{} & \colhead{} &  \colhead{}  & \colhead{parallax} & \colhead{$T_\mathrm{eff}$} & \colhead{$\log{g}$} & \colhead{Mass} & \colhead{Age} & \colhead{} \\
       \colhead{star} & \colhead{SpT} & \colhead{RA} & \colhead{DEC} &  \colhead{V} &   \colhead{
       (mas)} & \colhead{(K)} & \colhead{(cgs)} & \colhead{($M_{\odot}$)} & \colhead{(Myr)} & \colhead{Ref}
       }

@@

     HIP 813 &           B9Vn &    00:10:02.20 &   +11:08:44.93 &   5.537 &     10.68 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 1191 &          B8.5V &    00:14:54.52 &   -09:34:10.45 &   5.757 &      9.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 1366 &            A2V &    00:17:05.50 &   +38:40:53.89 &   4.610 &     10.56 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 1647 &            B9V &    00:20:39.04 &   -69:37:29.68 &   5.498 &     10.25 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 2381 &            A3V &    00:30:22.65 &   -23:47:15.65 &   5.190 &     18.83 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 2505 &           B8Vn &    00:31:46.36 &   +54:31:20.23 &   4.732 &      8.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 2548 &          B9.5V &    00:32:23.78 &   +06:57:19.66 &   5.698 &     12.35 &   $11864 \pm 403$ &  $4.4 \pm 0.14$ &  $2.8^{+0.16}_{-0.15}$ &     $78^{+70}_{-52}$ &      1 \\
    HIP 2912 &            B5V &    00:36:52.85 &   +33:43:09.64 &   4.360 &      5.45 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3300 &            B2V &    00:42:03.90 &   +50:30:45.09 &   4.810 &      2.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3478 &            B5V &    00:44:26.19 &   +47:51:50.34 &   5.646 &      5.23 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3741 &            B9V &    00:48:01.06 &   -21:43:20.99 &   5.570 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 3881 &            B5V &    00:49:48.85 &   +41:04:44.08 &   4.530 &      5.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 4436 &            A5V &    00:56:45.21 &   +38:29:57.64 &   3.870 &     25.14 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5131 &           A1Vn &    01:05:40.96 &   +21:28:23.45 &   5.317 &     11.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5132 &           A0Vn &    01:05:41.71 &   +21:27:55.60 &   5.532 &     11.64 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5310 &            A3V &    01:07:57.16 &   +20:44:20.83 &   5.569 &     21.14 &    $8611 \pm 293$ &  $4.4 \pm 0.14$ &  $1.8^{+0.10}_{-0.08}$ &  $307^{+234}_{-196}$ &      1 \\
    HIP 5348 &            B6V &    01:08:23.08 &   -55:14:44.73 &   3.967 &     10.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5361 &            B8V &    01:08:33.47 &   +58:15:48.41 &   5.773 &      5.41 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5518 &          A0Vnn &    01:10:39.32 &   +68:46:43.04 &   5.318 &     11.78 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 5626 &            A3V &    01:12:16.82 &   +79:40:26.27 &   5.600 &     12.07 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 7345 &            A1V &    01:34:37.78 &   -15:40:34.90 &   5.619 &     16.84 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 8016 &            B9V &    01:42:55.86 &   +70:37:21.09 &   5.177 &     11.75 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 8704 &          B1.5V &    01:51:59.32 &   +55:08:50.58 &   5.520 &      2.52 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
      HR 545 &          B9.5V &    01:53:31.77 &   +19:17:46.27 &   4.700 &   \nodata &  $11000 \pm 1000$ &  $4.3 \pm 0.25$ &  $2.5^{+0.39}_{-0.35}$ &    $37^{+105}_{-28}$ &  2 \\
    HIP 9312 &           A0Vn &    01:59:38.04 &   +64:37:17.76 &   5.283 &     13.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
    HIP 9564 &           A1Vn &    02:02:52.48 &   +64:54:05.27 &   5.999 &     11.92 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
      HR 604 &            B8V &    02:03:54.72 &   +42:19:51.41 &   5.820 &   \nodata &  $11000 \pm 1000$ &  $4.5 \pm 0.25$ &  $2.4^{+0.37}_{-0.34}$ &     $28^{+87}_{-20}$ &  2 \\
   HIP 10320 &            B9V &    02:12:54.47 &   -30:43:25.77 &   5.261 &     10.18 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 10670 &          A1Vnn &    02:17:18.87 &   +33:50:49.90 &   4.000 &     29.04 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 10732 &           A1Vn &    02:18:07.54 &   +19:54:04.19 &   5.575 &      7.29 &    $9500 \pm 300$ &  $4.0 \pm 0.25$ &  $2.1^{+0.18}_{-0.16}$ &    $80^{+237}_{-70}$ &  2 \\
   HIP 11345 &            A0V &    02:25:57.01 &   -12:17:25.71 &   4.869 &      7.15 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 12332 &            A7V &    02:38:48.99 &   +21:57:41.06 &   5.454 &      9.68 &    $7750 \pm 300$ &  $3.5 \pm 0.25$ &  $1.9^{+0.37}_{-0.30}$ &  $687^{+218}_{-425}$ &  2 \\
   HIP 12706 &           A2Vn &    02:43:18.04 &   +03:14:08.94 &   3.470 &     40.97 &    $8551 \pm 291$ &  $4.3 \pm 0.14$ &  $1.9^{+0.15}_{-0.12}$ &  $650^{+105}_{-188}$ &      1 \\
   HIP 12719 &            B3V &    02:43:27.11 &   +27:42:25.72 &   4.670 &      9.51 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 12803 &           B9Vn &    02:44:32.97 &   +15:18:42.71 &   5.776 &      5.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13165 &            B6V &    02:49:17.56 &   +17:27:51.52 &   5.314 &      4.18 &  $15000 \pm 1000$ &  $4.0 \pm 0.25$ &  $4.2^{+0.58}_{-0.50}$ &     $31^{+42}_{-22}$ &  2 \\
   HIP 13202 &            A0V &    02:49:54.18 &   -27:56:31.14 &   5.389 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13209 &           B8Vn &    02:49:59.03 &   +27:15:37.83 &   3.606 &     19.69 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13327 &            B7V &    02:51:29.59 &   +15:04:55.45 &   5.514 &      6.60 &  $15000 \pm 1000$ &  $4.5 \pm 0.25$ &  $4.0^{+0.50}_{-0.45}$ &      $15^{+26}_{-9}$ &  2 \\
   HIP 13717 &            A3V &    02:56:37.42 &   -03:42:44.35 &   5.160 &     17.49 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 13879 &           A2Vn &    02:58:45.67 &   +39:39:45.81 &   4.700 &     10.53 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14043 &            B7V &    03:00:52.21 &   +52:21:06.22 &   5.253 &      7.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14143 &            B7V &    03:02:22.52 &   +04:21:10.39 &   5.607 &      5.93 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14293 &            A5V &    03:04:16.52 &   -07:36:03.08 &   5.300 &     24.06 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 14576 &            B8V &    03:08:10.13 &   +40:57:20.33 &   2.120 &     36.27 &   $13070 \pm 444$ &  $4.0 \pm 0.14$ &  $3.6^{+0.28}_{-0.23}$ &    $139^{+16}_{-25}$ &      1 \\
   HIP 14764 &            B8V &    03:10:38.79 &   +11:52:21.44 &   5.965 &      7.33 &  $11750 \pm 1000$ &  $4.2 \pm 0.25$ &  $2.8^{+0.42}_{-0.39}$ &     $35^{+91}_{-27}$ &  2 \\
   HIP 14862 &          A2Vnn &    03:11:56.27 &   +74:23:37.17 &   4.840 &     19.72 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15110 &            A1V &    03:14:54.10 &   +21:02:40.01 &   4.880 &     12.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15338 &            B8V &    03:17:47.35 &   +44:01:30.08 &   5.478 &      4.46 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15404 &            B3V &    03:18:37.74 &   +50:13:19.83 &   5.158 &      5.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 15444 &            B5V &    03:19:07.64 &   +50:05:41.88 &   5.036 &      5.82 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16147 &            B5V &    03:28:03.07 &   +49:03:46.32 &   4.970 &      6.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16210 &           B6Vn &    03:28:52.33 &   +49:50:54.17 &   5.578 &      6.22 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16244 &            B3V &    03:29:22.05 &   +49:30:32.21 &   4.678 &      6.05 &  $16333 \pm 1000$ &  $4.3 \pm 0.25$ &  $4.7^{+0.57}_{-0.50}$ &      $15^{+22}_{-9}$ &  2 \\
   HIP 16285 &            A5V &    03:29:55.15 &   -42:38:03.32 &   5.768 &     15.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16322 &           A0Vn &    03:30:24.47 &   +11:20:11.19 &   5.125 &      9.03 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16340 &            B8V &    03:30:36.95 &   +48:06:12.95 &   5.820 &      3.65 &  $12500 \pm 1000$ &  $4.0 \pm 0.25$ &  $3.1^{+0.51}_{-0.42}$ &     $49^{+92}_{-39}$ &  2 \\
   HIP 16599 &            A3V &    03:33:39.06 &   +54:58:29.49 &   5.981 &     13.44 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 16611 &            B9V &    03:33:47.28 &   -21:37:58.38 &   4.300 &     11.12 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 17457 &            B7V &    03:44:30.51 &   -01:09:47.14 &   5.250 &      4.98 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 17527 &            B8V &    03:45:09.74 &   +24:50:21.34 &   5.640 &      7.97 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 17563 &            B3V &    03:45:40.44 &   +06:02:59.97 &   5.332 &      6.11 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 18141 &            B8V &    03:52:41.66 &   -05:21:40.54 &   5.476 &      5.57 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 18396 &            B6V &    03:55:58.17 &   +47:52:17.12 &   5.379 &      4.47 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 18724 &            B3V &    04:00:40.82 &   +12:29:25.22 &   3.410 &      6.74 &  $21000 \pm 1000$ &  $4.5 \pm 0.25$ &  $7.1^{+0.68}_{-0.64}$ &        $8^{+7}_{-3}$ &  2 \\
   HIP 18788 &            B5V &    04:01:32.05 &   -01:32:58.78 &   5.280 &      7.88 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 18805 &            B5V &    04:01:46.14 &   +09:59:52.84 &   5.676 &      5.71 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 19799 &           B9Vn &    04:14:36.23 &   +10:00:41.05 &   5.208 &      8.34 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 19949 &           A2Vn &    04:16:43.09 &   +53:36:42.47 &   5.200 &      9.98 &    $9825 \pm 334$ &  $3.8 \pm 0.14$ &  $2.2^{+0.11}_{-0.09}$ &  $199^{+135}_{-124}$ &      1 \\
   HIP 19968 &            B7V &    04:16:53.56 &   +61:50:59.97 &   5.700 &      7.31 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 20264 &            A0V &    04:20:39.01 &   -20:38:22.64 &   5.380 &      6.86 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 20380 &            A3V &    04:21:51.81 &   +56:30:22.74 &   5.920 &     10.31 &    $8738 \pm 297$ &  $3.9 \pm 0.14$ &  $1.9^{+0.10}_{-0.08}$ &  $331^{+213}_{-202}$ &      1 \\
   HIP 20430 &          B9Vnn &    04:22:34.94 &   +25:37:45.54 &   5.376 &     11.20 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 20507 &            A2V &    04:23:40.85 &   -03:44:43.68 &   5.171 &     15.60 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 20579 &            B8V &    04:24:29.16 &   +34:07:50.73 &   5.722 &      7.28 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 20789 &            B7V &    04:27:17.45 &   +22:59:46.80 &   5.515 &      8.63 &           \nodata &         \nodata &                \nodata &              \nodata &     \nodata \\
   HIP 21589 &            A6V &    04:38:09.46 &   +12:30:39.01 &   4.270 &     21.24 &    $8591 \pm 292$ &  $3.9 \pm 0.14$ &  $1.8^{+0.09}_{-0.07}$ &  $303^{+231}_{-193}$ &      1 \\
